Drug-target interaction (DTI) papers often use synthetic cold-start splits as proxies for generalization, but it remains unclear whether conclusions drawn from these splits transfer to real distribution shifts. We present a benchmark-first case study showing that, within an expanded five-model panel, rankings are highly sensitive to how the shift is defined. The panel contains a fully specified fixed-feature \texttt{base} encoder, a learner-control \texttt{RandomForest} baseline on the same Morgan+k-mer inputs, two recent pooled-LM baselines (\texttt{DTI-LM} and \texttt{HyperPCM}), and a \texttt{GraphDTA-style} graph-family probe. On a 3-seed synthetic reference panel built from \texttt{BindingDB\_Kd}, the winner depends strongly on the split: \texttt{RF} is strongest on \texttt{unseen\_drug} ($0.7339 \pm 0.0051$ \AUPRC{}) and \texttt{blind\_start} ($0.4512 \pm 0.0373$), while \texttt{base} remains strongest on \texttt{unseen\_target} ($0.5224 \pm 0.0602$). On the promoted temporal/provenance benchmarks, the ranking changes again. Over 3 seeds, \texttt{RF} becomes strongest on both \texttt{BindingDB\_patent / patent\_temporal} ($0.8234 \pm 0.0012$) and \texttt{BindingDB\_nonpatent\_Kd / nonpatent\_temporal} ($0.7201 \pm 0.0012$), with paired bootstrap intervals remaining strictly positive against both \texttt{base} and \texttt{DTI-LM}. In contrast, the \texttt{GraphDTA-style} probe is competitive but does not dominate any promoted axis. These additions strengthen the benchmark claim rather than weakening it: ranking instability is not confined to pooled-LM comparisons, and even a classical learner on fixed handcrafted inputs can become the strongest system under both synthetic and temporal evaluation. A pooled year-band and overlap-bucket diagnosis further shows that temporal/provenance OOD is structured rather than monolithic. We package the split manifests, benchmark resources, and standalone evaluator for reuse. Within the studied model panel and benchmarks, these results show that synthetic cold splits and real OOD shifts should not be treated as interchangeable evaluation settings for DTI.
