\section{Benchmark Setup}

Our goal is to test whether an expanded DTI model panel preserves its ranking across synthetic cold-start regimes and real distribution shifts. The panel used in the revised manuscript contains five models. \texttt{base} is a fixed-feature MLP reference system built from RDKit Morgan fingerprints and hashed protein k-mer features. \texttt{RF} is a learner-control \texttt{RandomForest} classifier trained on the exact same handcrafted pair representation as \texttt{base}, allowing us to separate the effect of the learner from the effect of the representation. \texttt{DTI-LM} is a pooled ChemBERTa+ESM2 baseline aligned to recent literature, \texttt{HyperPCM} is a task-conditioned pooled-LM baseline, and \texttt{GraphDTA-style} is a graph-family probe with a molecular GCN and protein CNN. We intentionally keep the panel modest rather than exhaustive, but it now spans fixed-feature neural, fixed-feature classical, pooled-LM, and graph-based inductive biases. Because the anchor system is central to every ranking claim, Appendix Table~\ref{tab:base-spec} gives the exact \texttt{base} feature construction, architecture, parameter count, and training recipe.

We evaluate this panel on two benchmark groups. The first is a synthetic reference panel based on \texttt{BindingDB\_Kd}, with three split definitions: \texttt{unseen\_drug}, \texttt{blind\_start}, and \texttt{unseen\_target}. The second is a real-OOD screening panel. Our primary real-OOD benchmark is the BindingDB patent split (\texttt{patent\_temporal}), which uses a year-based temporal partition and is evaluated over three seeds. We also include \texttt{BindingDB\_Ki / unseen\_target} and \texttt{DAVIS / unseen\_target} as supporting shifted target-cold benchmarks that test whether the same external model family remains stable across assay and dataset shifts. Table~\ref{tab:taxonomy} summarizes the shift taxonomy and split statistics.

\input{tables/table_taxonomy}

We report \AUPRC{} as the primary metric and \AUROC{} as a secondary metric. \AUPRC{} is emphasized because class balance and ranking behavior are central to the benchmark claims in this paper. For the expanded panel, we report matched three-seed results on the synthetic reference panel and the promoted temporal benchmarks. We first run transparent seed0 screening for the newly added baselines, then promote them where the screening result is either strong enough to affect the panel story or informative enough to test a reviewer concern. \texttt{RF} is promoted on all main and temporal axes because its seed0 performance is unexpectedly strong across the board. \texttt{GraphDTA-style} is promoted on \texttt{unseen\_drug}, \texttt{unseen\_target}, \texttt{patent\_temporal}, and \texttt{nonpatent\_temporal} because these are the axes most relevant to the benchmark claims and to the request for a graph-based family. Appendix Table~\ref{tab:recent-screening} and the baseline-expansion report make this promotion logic explicit. We further add paired bootstrap uncertainty support for the headline expanded-panel comparisons, especially those involving \texttt{RF} on synthetic drug-cold, blind-start, and the temporal benchmarks. Appendix Table~\ref{tab:bootstrap-summary} collects these intervals.

To make the benchmark reusable, each split is exported as a canonical resource bundle with manifests, split tables, cached identifiers, and a standalone CSV-based evaluator. This resource layer allows external predictions to be scored against the exact same test partitions used in the paper. Appendix Table~\ref{tab:resource-release} enumerates the released artifacts and how they are consumed by the evaluator.

The patent benchmark requires several setup choices that are documented explicitly. We use a local year-based split of \texttt{BindingDB\_patent}, with training years before the validation year, a held-out validation year, and a later temporal test set. Because this benchmark also changes provenance and assay composition, we describe it as temporal/provenance OOD rather than pure time shift. We also use a patent-specific affinity conversion rather than reusing the standard \texttt{pKd} transform, because the patent benchmark stores affinities in a different log-scale convention. Appendix Table~\ref{tab:patent-spec} summarizes the exact year boundaries, split counts, label construction, overlap policy, and seed semantics for both \texttt{patent\_temporal} and the alternative-cutoff \texttt{patent\_temporal\_v2017}. Appendix Table~\ref{tab:nonpatent-spec} provides the same information for the review-driven \texttt{BindingDB\_nonpatent\_Kd / nonpatent\_temporal} probe. BindingDB-derived panels are anchored in the BindingDB resource \citep{liu2007bindingdb}, while DAVIS provides an external kinase-focused support benchmark \citep{davis2011kinase}.

Finally, for diagnostic analysis, we use the saved overlap score from each test prediction to compute overlap buckets that summarize how strongly each test example resembles the training support. Concretely, \texttt{overlap\_score} is defined as $\min(s_d, s_t)$, where $s_d$ is the cosine similarity between the test drug's Morgan fingerprint and its nearest training-drug neighbor, and $s_t$ is the cosine similarity between the test target's hashed k-mer feature vector and its nearest training-target neighbor. We use the minimum to conservatively define overlap: a pair is high-overlap only when both its drug and target are well represented in the training set. We retain cosine for the released overlap score so that drug-side and target-side overlap share the same similarity scale inside this joint diagnostic; the separate synthetic similarity analysis still reports the standard Morgan-fingerprint Tanimoto and scaffold-overlap statistics. We report benchmark taxonomy and split statistics, including test-set size and prevalence, so that \AUPRC{} is interpreted within benchmark rather than across benchmark families.
