\section{Appendix}

\subsection{Patent benchmark specification}

Because the main paper depends on \texttt{BindingDB\_patent / patent\_temporal}, we make its construction explicit here. Table~\ref{tab:patent-spec} enumerates the year boundaries, split counts, label construction, overlap policy, and seed semantics for both the main patent split and the earlier-cutoff robustness variant.

\input{tables/table_patent_spec}

\subsection{Non-patent temporal probe specification}

Because the main revision also relies on \texttt{BindingDB\_nonpatent\_Kd / nonpatent\_temporal} to separate temporal drift from patent provenance, we make that construction explicit as well. Table~\ref{tab:nonpatent-spec} lists the source file, year cutoffs, label transform, prevalence, duplicate policy, and seed semantics for the released non-patent temporal split.

\input{tables/table_nonpatent_spec}

\subsection{Reference-model specification}

Because every ranking claim is anchored against \texttt{base}, we make that system explicit rather than treating it as an unnamed baseline. Table~\ref{tab:base-spec} specifies the exact input features, network structure, parameter count, optimization recipe, and implementation path used in every experiment.

\input{tables/table_base_spec}

\subsection{Promoted learner-control and graph-family specifications}

Because the expanded panel now hinges on the \texttt{RF} learner-control baseline and the \texttt{GraphDTA-style} graph-family probe, we make those systems explicit as well. Table~\ref{tab:graph-spec} mirrors the level of detail used for \texttt{base}, and also records the core \texttt{RF} hyperparameters that produced the promoted results.

\input{tables/table_graph_spec}

\subsection{Additional real-OOD support benchmarks}

The main paper focuses on the strongest evidence chain: the synthetic \texttt{BindingDB\_Kd} reference panel, the promoted temporal benchmarks, and the patent year/overlap diagnosis. \texttt{BindingDB\_Ki} and \texttt{DAVIS} remain supporting real-OOD benchmarks: both now use matched 3-seed evaluation, but they reinforce rather than replace the temporal story. To keep the promotion budget focused on the most decision-relevant axes, the support table keeps the promoted external baselines rather than rerunning the full five-model panel.

\input{tables/table_support_benchmarks}

On the \texttt{BindingDB\_Ki} support split, Table~\ref{tab:support} shows that \texttt{base} remains ahead of both \texttt{DTI-LM} and \texttt{HyperPCM}. On \texttt{DAVIS}, \texttt{base} and \texttt{DTI-LM} are nearly tied on mean \AUPRC{}, but \texttt{base} stays slightly higher on the paper's primary ranking metric. Together, these support panels reinforce the main message that strong recent baselines do not transfer uniformly across OOD definitions.

\subsection{Review-driven robustness probes}

The external review highlighted two concrete risks: that the promoted patent result might be driven mainly by provenance rather than temporal shift, and that the synthetic \texttt{unseen\_drug} split might still be chemically too permissive. Table~\ref{tab:robustness-probes} records the targeted fixes. The first probe constructs a non-patent temporal benchmark directly from the official BindingDB release and shows that even before the learner-control expansion, \texttt{DTI-LM} stays ahead of \texttt{base} over matched 3-seed evaluation. The second probe replaces entity holdout with a Murcko-scaffold holdout and shows that the original synthetic \texttt{HyperPCM} edge does not survive this stricter split. We further add two controlled patent variants that explicitly suppress recurrent train pairs or seen-drug overlap. These do not erase the benchmark-sensitivity finding. Instead, they sharpen it: under \texttt{patent\_temporal\_pair\_novel} and \texttt{patent\_temporal\_drug\_novel}, the AUPRC winner changes again, with \texttt{DTI-LM} overtaking \texttt{RF} while \texttt{RF - base} becomes unreliable on the pair-novel variant.

\input{tables/table_robustness_probes}

\subsection{Paired uncertainty support}

Table~\ref{tab:bootstrap-summary} summarizes the paired bootstrap intervals for the expanded-panel comparisons. The strongest supported deltas still include the learner-control baseline on synthetic \texttt{unseen\_drug}, \texttt{blind\_start}, and the aggregate patent and non-patent temporal benchmarks. At the same time, the controlled patent rows show why the paper should not overstate that temporal story. \texttt{RF - base} on \texttt{patent\_pair\_novel} crosses zero, while \texttt{DTI-LM - RF} is strictly positive on both controlled patent variants. By contrast, the synthetic \texttt{unseen\_target} comparison \texttt{RF - base} also crosses zero, and the scaffold-split \texttt{HyperPCM - base} comparison crosses zero as well, which is exactly why those rows are described conservatively in the main text.

\input{tables/table_bootstrap_summary}

\subsection{Expanded-panel screening and promotion}

To avoid cherry-picking concerns, Table~\ref{tab:recent-screening} summarizes the seed0 screening passes used to decide which additional baselines to promote. The early external-baseline screen prioritized the strongest recent model on the primary real-OOD benchmark \texttt{patent\_temporal}; the later panel-expansion screen then added the learner-control and graph-family probes and promoted whichever systems materially changed the main synthetic or temporal read.

\input{tables/table_recent_screening}

\subsection{Reusable benchmark resources}

The benchmark release is intended to be reused independently of the in-repo models. Table~\ref{tab:resource-release} lists the concrete artifacts exported for each split and how they interact with the standalone evaluator. In practice, an external user only needs the canonical split bundle plus a prediction CSV keyed by \texttt{example\_id}; the evaluator then reproduces the same global metrics and overlap-bucket metrics reported in this paper.

\input{tables/table_resource_release}

\subsection{Method-centric ablations}

Earlier project stages explored routers, conservative target-memory variants, and selective fallback rules. These analyses were useful for method diagnosis, but they do not define the final paper narrative. The benchmark paper is intentionally centered on ranking instability across shift definitions rather than on proposing a new best-performing method.
